### 2019-02-26 sections/abstract.tex
some fixmes
focus on non-programmers leads to inflexibility

% Context
Software that models how people work is omnipresent in today's society.
Current languages and frameworks are limited in flexibility and lack a good level of abstraction.
Task-oriented programming (TOP) is a programming paradigm that aims to provide the desired level of abstraction while still being expressive enough to describe real world collaboration.
It prescribes a declarative programming style to specify multi-user workflows.
Workflows can be higher-order.
They communicate through typed values on a local and global level.
Such specifications can be turned into interactive applications for different platforms, supporting collaboration during execution.

% Inquiry
TOP has been around for more than a decade, in the form of iTasks, which is tailored for real-world usability.
So far, it has not been given a formalization in the style common in programming language research.

>>>>

% Context
Software that models how people work is omnipresent in today's society.
Current languages and frameworks often focus on usability by non-programmers, sacrificing flexibility and high level of abstraction.
Task-oriented programming (TOP) is a programming paradigm that aims to provide the desired level of abstraction while still being expressive enough to describe real world collaboration.
It prescribes a declarative programming style to specify multi-user workflows.
Workflows can be higher-order.
They communicate through typed values on a local and global level.
Such specifications can be turned into interactive applications for different platforms, supporting collaboration during execution.

% Inquiry
TOP has been around for more than a decade, in the form of iTasks, which is tailored for real-world usability.
So far, it has not been given a formalization which is very suitable for formal reasoning.
